Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-11-20 ijar-npb-ms.tex
elicitation ideas

In this near-noninformative setting, the choice of $\nktzl$ not relevant,
as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Logically, one cannot have prior-data conflict in case of prior near ignorance.

@@

***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$?
What if we know, e.g., pretty much what's going on for low $t$
but want to be much more cautious for high $t$?
$\yktzl$ can then drop to 0, but are we ok that $\yktzu$ cannot increase?
(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
but does this need to hold for the prior guess range bound $\yktzu$?)***

@@

>>>>

In this near-noninformative setting, the choice of $\nktzl$ is not relevant,
as both $\yktnl$ and $\yktnu$ are obtained with $\nktzu$;
indeed $\yktzl > 0$ and $\yktzu < 1$ can be chosen such that
$\frac{s^k_t}{n_k} \in [\yktzl, \yktzu]$ for all $t \in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
Logically, one cannot have prior-data conflict in case of prior near ignorance.

@@

***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
If we know, e.g., pretty much what's going on for low $t$
but want to be much more cautious for high $t$,
then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.
Better to express certainty of prior guess via $\nktz$ bounds?
With strongly differing $\nktz$ values, it could however happen that, e.g., $\yzu_{k,t_j} \le \yzu_{k,t_{j+1}}$!
So require same $\nktz$ bounds for all $t$?
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***

@@

***we should also cover the case where $\yktz$ bounds are not given for all $t \in {\cal T}$,
as it will be too time-consuming to elicit $\yktz$ bounds for all $t$ in a dense grid.
(Calculating $\Rsys(t)$ for a too coarse grid only will waste information from data.)
Idea: ``fill up the $t$ grid at all $t$'' with least-committal bounds, i.e.: 
at all $t$ not elicited, take $\yktzu$ equal to last (in time sequence) elicited $\yktzu$,
and $\yktzl$ equal to next (in time sequence) elicited $\yktzl$.

***possible elicitation procedure: starting with $\yktz$ bounds for `middle' or `typical' $t$,
then $\yktz$ bounds for $t$ smaller than `middle' $t$ (or halfway between 0 and `middle' $t$?) and for $t$ larger than `middle' $t$,
refine further as possible.
